[dcpo_demsupport]

### 2020-08-08 paper/dcpo_demsupport.Rmd
estimates of model 1-4; per #9

## Windmeijer corrected standard errors
vcovHC_se <- function(x) {
  plm::vcovHC(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

@@

@@

@@

>>>>

## Windmeijer corrected standard errors
vcovHC_se <- function(x) {
  plm::vcovHC(x) %>% 
    diag() %>% 
    sqrt()
}

@@

save(df_result_dcpo, file = here::here("output", "estimates_cls.RDS"))
```

@@

  result_betas_dcpo_1k <-
    mitools::MIextract(result_dcpo_1k, fun = coef)

@@

df_result_dcpo[4] <- map(mod_ls[[2]], estimate_dcpo, aType = "gmm")

save(df_result_dcpo, file = here::here("output", "estimates_dcpo.RDS"))
```
